### 2016-09-17 conclusions.tex
Some more corrections up to the conclusions

\label{sec:conclusions}
Observing the expectation of the \ac{IoT} and lack for a low-cost, easy to configure testbed that enables reproducible results for mechanisms to address problems in this area, we provide a in-depth description of the new Aalborg University's \ac{Raspi} testbed for network coding evaluation and how to guarantee replicability and scaling managing of this system. The description shows how to set up interconnected \ac{Raspi}s with memory cards for local storage, a Raspbian Lite image, network connectivity and proper system administration privileges. We hope this work permits researchers to replicate setups and scenarios for evaluating their strategies in a rapid and manageable way. Future work in the use of \ac{Raspi} devices will focus on expanding the setup and automation of tasks to run the testbed, configure specified network topologies (e.g., with specific connectivity or packet loss ratios), reserve the use of these sub-networks for running tailored experiments and opening the use of the testbed beyond our team at Aalborg University.

>>>>

\label{sec:conclusions}
Observing the expectation of the \ac{IoT} and lack for a low-cost, easy-to-configure testbed in this area for reproducible research, we provide an in-depth description of the new Aalborg University's \ac{Raspi} testbed for network coding evaluation and how to guarantee replicability and scaling managing of this system. The description shows how to set up interconnected \ac{Raspi}s with memory cards for local storage, a Raspbian Lite image, network connectivity and proper system administration privileges. Using the presented procedure permits to setup a Raspbian Lite for the \ac{Raspi}s, but this restrics the testbed administrators to specifically using this \ac{OS}. Other Linux distributions might be setup with Yocto \todot{Include this as a pro/con? Nestor: Here I would say that a good idea to address this comment is to compare our approach with another one :)} to create an image from the scratch, but that goes beyond the scope of this procedure.  We hope this work permits researchers to replicate setups and scenarios for evaluating their strategies in a rapid and manageable way. Future work in the use of \ac{Raspi} devices will focus on expanding the setup and automation of tasks to run the testbed, configure specified network topologies (e.g., with specific connectivity or packet loss ratios), reserve the use of these sub-networks for running tailored experiments and opening the use of the testbed beyond our team at Aalborg University. Future work in this area will consider to make the testbed fetch the image through the \ac{HTTP} server. This is expected to simplify the maintenance of the memory cards.

### 2016-09-17 cross_compilation.tex
Corrections
Some more corrections up to the conclusions

\subsection{Toolchain Setup}
To compile in a given architecture that is aimed for a different one,
the testbed administrator needs to install a toolchain in its \ac{PC}.
The toolchain is mandatory due to the different processor architectures
where the source can be compiled from.
Given that compiling a toolchaing can be an ardous task, we get the toolchain
recommended for the \ac{ARM} architecture of the \ac{Raspi}s.
This toolchain is available from \cite{2016rpitoolchain} and
it already contains the binaries for different compilers based on
\texttt{gcc 4.9}. In what follows, we extract the binaries adjusting
them to our coding style and compiling convention. For this, we use the
\texttt{\$\{TOOLCHAIN\}} directory as the working directory.
The testbed administrator may choose some other working directory of
its preference if desired. First, we create the toolchain directory:

@@

Later, we download the \ac{Raspi} toolchain for 64-bit Linux.
Instead of working with the binaries from \cite{2016rpitoolchain},
we use a zipped version with the original binaries and renamed symbolic
links to the original files available in
\cite{2016steinwurfrpitoolchain}. Finally, we unzip the downloaded file.
This is made as follows:

@@

This should produce a binary \texttt{hello\_world} that is executable
in the \ac{Raspi}. We copy it to a \ac{Raspi} to test it. We will
use \ac{SCP} to copy the binary file to one of the \ac{Raspi}s.
%Still, we for example might use Fabric if we are interested in deploying
Still, we might use Fabric instead if we are interested in deploying
a compiled binary for many \ac{Raspi}s.

>>>>

\subsection{Toolchain Setup}
To compile in a given architecture that is aimed for a different one,
the testbed administrator needs to install a toolchain in its \ac{PC}.
The toolchain is mandatory due to the different processor architectures
where the source can be compiled from.
Given that compiling a toolchaing can be an arduous task, we get the toolchain
recommended for the \ac{ARM} architecture of the \ac{Raspi}s.
This toolchain is available from \cite{2016steinwurfrpitoolchain} and
it already contains the binaries for different compilers based on
\texttt{gcc 4.9}. In what follows, we extract the binaries adjusting
them to our coding style and compiling convention. For this, we use the
\texttt{\$\{TOOLCHAIN\}} directory as the working directory.
The testbed administrator may choose some other working directory of
its preference if desired. First, we create the toolchain directory:

@@

Later, we download a \ac{Raspi} toolchain with the binaries for a 64-bit Linux
distribution available in \cite{2016steinwurfrpitoolchain}. Finally, we unzip the
downloaded file. This is made as follows:

@@

This should produce a binary \texttt{hello\_world} that is executable
on the \ac{Raspi}. We copy it to a \ac{Raspi} using \ac{SCP} and using
Fabric instead if we are interested in deploying a compiled binary for
many \ac{Raspi}s.
